Climate Prediction Markets and the Convergence of Forecasting Models: An Agent-Based Simulation

### 2016-03-01 paper.Rmd
paper

Traders use one of the two models to forecast future temperatures. These models are interpreted as the trader's beliefs about the true climate process, i.e. the driving factors of long-term global temperatures. They represent pervasive positions on climate change in the public debate. In order to approximatively match the current configuration of beliefs in climate change in the United States, model 1 is randomly assigned to half of the traders, while 2 is assigned to the other half of the traders.

Thus, both when **true.model** = 0 and **true.model** = 1,  some traders use the true data-generating model to make predictions. However, this does not mean that traders using the true model make perfectly accurate predictions. Although these traders believe in the correct *functional form* of the model, they still need to calibrate it based on limited noisy data. Therefore, the values they use as the parameters of the model will typically still be different from the exact parameters of the data-generating process.

@@

Based on their reservation price, traders behave as "zero-intelligence" agents [@Gode1993], that is, they sell at a random price above their reservation, and buy at a random price below their reservation. The distribution from which buy and sell prices are drawn is determined by the traders risk attitude, characterized by parameter $risk.tak_i$. These strategies are simple but have been shown to provide accurate approximations of behavior in prediction markets (see for instance @Klingert2012c), and in financial markets more broadly.

Continuous-double auctions (CDAs) or some variants thereof are common market mechanisms, i.e. procedures to match buy and sell orders. CDA are notably used on large stock markets [@Tseng2010a]. Our model features a particular version of CDA through which traders exchange securities.

@@

Traders are part of a social network. Jonathan - add in changes made to social network. Every time a security is realized, each trader $i$ looks at the performance of their neighbors in the network. If one of $i$'s neighbors, say $j$, is richer than $i$, $i$ interprets this has an indication that $j$ has a better approximate model. Then $i$ considers adopting $j$'s approximate model. Traders start with the same initial amount of money, so differences in money among traders can only come from  traders' interactions through the market. For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is characterized by parameter $ideo_i$.

@@

# Model Parameters

>>>>

Traders use one of the two models to forecast future temperature anomalies. These models are interpreted as the trader's beliefs about the true climate process, the driving factor of long-term global temperatures. They represent pervasive positions on climate change in the public debate. In order to approximatively match the current configuration of beliefs in climate change in the United States, model 1 is randomly assigned to half of the traders, while 2 is assigned to the other half of the traders.

Thus, both when **true.model** = 0 and **true.model** = 1, approximately half of the traders use the true data-generating model to make predictions. However, traders using the true model do not necessarily make perfectly accurate predictions. Although these traders believe in the correct *functional form* of the model, they still need to calibrate it based on limited noisy data. Therefore, the values they use as the parameters of the model will typically still be different from the exact parameters of the data-generating process.

@@

Based on their reservation price, traders behave as "zero-intelligence" agents [@Gode1993], that is, they sell at a random price above their reservation, and buy at a random price below their reservation. The distribution from which buy and sell prices are drawn is determined by the traders risk attitude, characterized by parameter $risk.tak_i$. These trading strategies are simple but have been shown to provide accurate approximations of behavior in prediction markets [@Klingert2012c], and in financial markets more broadly.

Our model features a particular version of CDA through which traders exchange securities. Continuous-double auctions (CDAs) or some variants thereof are common market mechanisms, i.e. procedures to match buy and sell orders. CDA are notably used on large stock markets [@Tseng2010a].

@@

Traders are part of a social network where each agent forms two links at random, and then forms links randomly. This ensures that each agent is connected to at least two other agents. Every time a security is realized, each trader $i$ looks at the performance of their neighbors in the network. If one of $i$'s neighbors, say $j$, is richer than $i$, $i$ interprets this has an indication that $j$ has a better approximate model. Then $i$ considers adopting $j$'s approximate model. Traders start with the same initial amount of money, so differences in money among traders can only come from  traders' interactions through the market. For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is characterized by parameter $ideo_i$.

@@

## Model Parameters
